An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-02-08 tex/paper.tex
Correct references + tidying images
- Adding references for the web links
- Grouping some images together

\usepackage{amsmath}  % Basic
\usepackage{hyperref}  % Links etc
\usepackage{booktabs}  % Better tables
\usepackage{minted}  % Code
\usepackage{graphicx}  % Images

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/demo_tournament.pdf}
    \caption{The results from a simple tournament.}
    \label{fig:demo_tournament}
\end{figure}

@@

As stated in Section~\ref{sec:introduction} one of the main goals of the library
is to allow for the easy contribution of strategies. To do this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.
You can see an overview of the structure of the source code in Figure~\ref{fig:overview}.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/outline_of_library.pdf}
    \caption{An overview of the source code.}
    \label{fig:overview}
\end{figure}

To date the library has had contributions from 24 contributors from a variety of
backgrounds. These contributions have both been in terms of strategies (one
strategy is the creation of an undergraduate mathematics student with little
prior knowledge of programming) as well as the architecture of the library
itself.

@@

\begin{figure}[!hbtp] \centering
    \includegraphics[width=.8\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
    \caption{The number of strategies included in the library}
    \label{fig:number_of_strategies_against_date}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/stewart_tournament.pdf}
    \caption{The results from \cite{Stewart2012}.}
    \label{fig:stewart_tournament}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/tournament.pdf}
    \caption{Results from the library tournament (2015-12-19)}
    \label{fig:tournament}
\end{figure}

The current winning strategy is a novel strategy called: Looker Up. This
is a strategy that maps a given set of states to actions. The state space is
defined generically by \(m, n\) so as to map states to actions in the following
way:

\[(\underbrace{(C, D, D, D, C, D, D, C)}_{m\text{ first actions by opponent}},
\overbrace{((C, C), (C, C))}^{n\text{ last pairs of actions}}) \to D\]

The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
Intuitively, this state space uses the initial plays of the opponent to gain
some information about its intentions whilst still taking in to account the
recent play. The actual winning strategy is an instance of the framework for
\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
details of this can be found at
\url{http://mojones.net/evolving-strategies-for-an-iterated-prisoners-dilemma-tournament.html}.
At
\url{http://vknight.org/unpeudemath/gametheory/2015/11/28/Experimenting-with-a-high-performing-evolved-strategy-in-other-environments/}
experiments are described that evaluate how this particular strategy behaves in
environments other than those in which it was trained\dots

@@

Details for the above can be found at \url{http://marcharper.codes/}.

>>>>

\usepackage{amsmath}  % Basic
\usepackage{hyperref}  % Links etc
\usepackage{booktabs}  % Better tables
\usepackage{minted}  % Code
\usepackage{graphicx}  % Images
\usepackage{subcaption}  % Subfigures

@@

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/demo_tournament.pdf}
		\caption{The results from a simple tournament.}
		\label{fig:demo_tournament}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/stewart_tournament.pdf}
		\caption{The results from \cite{Stewart2012}.}
		\label{fig:stewart_tournament}
	\end{subfigure}
	\caption{Summary plots produced by the library.}
\end{figure}

@@

As stated in Section~\ref{sec:introduction} one of the main goals of the library
is to allow for the easy contribution of strategies. To do this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

To date the library has had contributions from 24 contributors from a variety
of backgrounds. These contributions have both been in terms of strategies (one
strategy is the creation of an undergraduate mathematics student with little
prior knowledge of programming) as well as the architecture of the library
itself. You can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/outline_of_library.pdf}
		\caption{An overview of the source code.}
		\label{fig:overview}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
		\caption{The number of strategies included in the library}
		\label{fig:number_of_strategies_against_date}
	\end{subfigure}
	\caption{An overview of the library.}
\end{figure}

@@

@@

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
	\caption{Results from the library tournament (2015-12-19)}
	\label{fig:tournament}
\end{figure}

The current winning strategy is a novel strategy called: Looker Up. This is a
strategy that maps a given set of states to actions. The state space is defined
generically by \(m, n\) so as to map states to actions as shown
in~(\ref{equ:example_of_lookerup}).

\begin{equation}
	(\underbrace{(C, D, D, D, C, D, D, C)}_{m\text{ first actions by opponent}},
	\overbrace{((C, C), (C, C))}^{n\text{ last pairs of actions}}) \to D
	\label{equ:example_of_lookerup}
\end{equation}

The above example is an incomplete illustration of the mapping for \(m=8,
n=2\). Intuitively, this state space uses the initial plays of the opponent to
gain some information about its intentions whilst still taking in to account
the recent play. The actual winning strategy is an instance of the framework
for \(m=n=2\) for which an evolutionary algorithm has been used to train it.
More details of this can be found in \cite{Jones2015}. In \cite{Knight2015}
experiments are described that evaluate how this particular strategy behaves in
environments other than those in which it was trained and it continues to
perform strongly.

@@

Details for the above can be found in \cite{Harper2015}.
